251 MA

### 2023-02-10 code/process.Rmd
fix directionality

# Exclusions

@@

- "reproduction" -- student did a reproduction and not replication

@@

# Parsing

@@

parse_t <- function(tval, within_between) {
  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pt(q=val, df=df, lower.tail=FALSE)*2
  d_calc=NA
  N_from_df=NA
  if(within_between=="between"){
    d_calc=2*val/(sqrt(df))  # note this uses the 2t/sqrt(df) approximation df+2 might be more appropriate? 
    N_from_df=df+2 # between so add 2
  }
  else{
    d_calc=val/sqrt(df)
    N_from_df=df+1
  }
  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
}
```

```{r}
parse_f <- function(fval, within_between){
  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
  d_calc=NA
  N_from_df=df_1+df_2+1
  if(!is.na(df_1)&&df_1==1){
    if(within_between=="between"){
      d_calc=2*sqrt(val)/sqrt(df_2) # if there's just two groups, then F=t**2 and we can use the t-test thingy
    }
    else{
      d_calc=sqrt(val)/sqrt(df_2)
    }
  }
  else if(!is.na(df_1)){
    # we go through partial eta
    n=df_1+df_2+1 # rederive n b/c it's not always matching the n we have
    partial_eta=(val*df_1)/(val*df_1+df_2)
    d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
  }
  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=NA, "SE"=NA))
}
```

```{r}
# for proportions 
#ex <- "prob: 13 / 14 , 2 / 14"
parse_prop <- function(propval){
  val <- str_extract_all(propval, "[0-9]+")[[1]]
  num1 <- val[1] |> as.numeric()
  den1 <- val[2] |> as.numeric()
  num2 <- val[3] |> as.numeric()
  den2 <- val[4] |> as.numeric()
  est1 <- num1/den1
  est1_var <- est1*(1-est1)/den1
  est2 <- num2/den2
  est2_var <- est2*(1-est2)/den2
  diff <- est1-est2
  diff_var <- est1_var+est2_var
  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=diff, "SE"=sqrt(diff_var)))
}
#parse_prop(ex)

@@

```{r}
parse_mean_ci <- function(mci,within_between,n){
  cond1=str_extract(mci, "m1.*\\],")
  cond2=str_extract(mci, "m2.*\\]")
  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se1=high1-low1/(2*1.96)
  se2=high2-low2/(2*1.96)
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=NA, "SE"=NA))
}
```

```{r}
parse_mean_sd <- function(msd,within_between,n){
  cond1=str_extract(msd, "m1.*\\),")
  cond2=str_extract(msd, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  sd_pool=(sd1+sd2)/2
  se=sd_pool/sqrt(n)
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=NA, "SE"=NA))
}

@@

```{r}
parse_mean_se <- function(mse,within_between,n){
  cond1=str_extract(mse, "m1.*\\),")
  cond2=str_extract(mse, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=NA, "SE"=NA))
}

@@

@@

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=NA, "SE"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,4)=="prop"){return(parse_prop(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_ci(raw_stat))}

@@

## Compare pvals

@@

Where there's a difference, I could check whether it's being compared to something *I* calculated versus something that an original paper or students paper calculated? Except that there's sources for errors in any of those. Ones where we get an off  by two error -- should I double check within-betweeness for the test?

## what didn't parse

@@

test |> filter(is.na(target_d_calc)&is.na(target_beta)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)

test |> filter(is.na(rep_d_calc)&is.na(rep_beta)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
```

## how are the df's lining up with sample size?

@@

@@

# PredInt and P_orig

d_es <-  test |> 
  rowwise() |> 
  mutate(target_se_calc=est_SE(target_p_calc,target_d_calc),
         rep_d_calc=ifelse(same_dir=="no", -rep_d_calc, rep_d_calc),
         rep_se_calc=est_SE(rep_p_calc,rep_d_calc))

```{r}
do_pred_int <- function(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE){
  if (!is.na(target_d_calc)&!is.na(rep_d_calc)){
    return(Replicate::pred_int(target_d_calc,target_se_calc**2, rep_d_calc, rep_se_calc**2)$rep.inside)}
  if(!is.na(target_beta)&!is.na(rep_beta)){
    return(Replicate::pred_int(target_beta, target_SE**2, rep_beta, rep_SE**2)$rep.inside)
  }
  return(NA)
}

do_p_orig <- function(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE){
  if (!is.na(target_d_calc)&!is.na(rep_d_calc)){
    return(Replicate::p_orig(target_d_calc,target_se_calc**2, rep_d_calc, t2=0, rep_se_calc**2))}
  if(!is.na(target_beta)&!is.na(rep_beta)){
    return(Replicate::p_orig(target_beta, target_SE**2,rep_beta, t2=0, rep_SE**2))
  }
  return(NA)
}

do_subjective_rep <- function(replicated_instructor_code, replicated_report_code, adjudicated_replication_code){
  if (is.na(replicated_instructor_code)){return(as.numeric(NA))}
  if (is.na(replicated_report_code)){return(as.numeric(NA))}
  if (replicated_instructor_code==replicated_report_code){ return(replicated_instructor_code)}
  if (!is.na(adjudicated_replication_code)){return (adjudicated_replication_code)}
  return(as.numeric(NA))
}
d_es_predInt <- d_es |> 
         mutate(
           predInt=do_pred_int(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE),
           p_orig=do_p_orig(target_d_calc, target_se_calc, rep_d_calc,rep_se_calc, target_beta, target_SE, rep_beta, rep_SE),
           sub_rep= do_subjective_rep(replicated_instructor_code, replicated_report_code, adjudicated_replication_code))

@@

d_check_nas |> filter(if_any(everything(), ~is.na(.)))

d_check_nas |> filter(across(everything(), ~!is.na(.)))

d_check_nas  |> select(target_lastauthor_year, status, academic_year, target_year,
           stanford_internal,open_data, open_materials, target_on_turk,
           replication_on_turk, within_between, single_vignette, repeated_measure,
           target_N, replication_N, predInt, p_orig) |>  filter(if_any(everything(), ~is.na(.)))
```

@@

>>>>

```
<!--
# Exclusions

@@

- "reproduction" -- student did a reproduction and not replication 
-->

@@

```{r}
#helper function for pooling when needed
pool_m_sd <- function(m1, sd1, n1, m2, sd2, n2){
  m=(m1*n1+m2*n2)/(n1+n2)
  var=(n1*(sd1**2+m1**2)+n2*(sd2**2+m2**2))/(n1+n2)-m**2
  sd=sqrt(var)
  return(c(m,sd))

}

#pool_m_sd(2.875,1.3102163,16,3.5,.8548504,14)
#pool_m_sd(1.5, 1.6329932, 16, 2.25, 1.6583124, 12)
#pool_m_sd(2.48,1.41,46,3.35,1.07,49)
#pool_m_sd(1.90,1.54,49,2.22,1.46,49)
```
# Parsing

@@

parse_t <- function(tval, within_between) {
  df=str_extract(tval, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(tval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pt(q=val, df=df, lower.tail=FALSE)*2
  d_calc=NA
  N_from_df=NA
  if(within_between=="between"){
    d_calc=2*val/(sqrt(df))  # note this uses the 2t/sqrt(df) approximation df+2 might be more appropriate? 
    N_from_df=df+2 # between so add 2
  }
  else{
    d_calc=val/sqrt(df)
    N_from_df=df+1
  }
  se=est_SE(pval, d_calc)
  return(data.frame("df_1"=NA, "df_2"=df,"tstat"=val, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
}
```

```{r}
parse_f <- function(fval, within_between){
  df_1 =str_extract(fval, "\\(.*,") |> str_sub(2,-2) |> as.numeric()
  df_2 =str_extract(fval, ",.*\\)") |> str_sub(2,-2) |> as.numeric()
  val=str_extract(fval, "=.*") |> str_sub(2,-1) |> as.numeric() |> abs()
  pval=pf(q=val, df1=df_1, df2=df_2, lower.tail=FALSE)
  d_calc=NA
  N_from_df=df_1+df_2+1
  if(!is.na(df_1)&&df_1==1){
    if(within_between=="between"){
      d_calc=2*sqrt(val)/sqrt(df_2) # if there's just two groups, then F=t**2 and we can use the t-test thingy
    }
    else{
      d_calc=sqrt(val)/sqrt(df_2)
    }
    se=est_SE(pval,d_calc)
  }
  else if(!is.na(df_1)){
    # we go through partial eta
    n=df_1+df_2+1 # rederive n b/c it's not always matching the n we have
    #partial_eta=(val*df_1)/(val*df_1+df_2)
    #d_calc=sqrt(n/(n-1)*(partial_eta/(1-partial_eta)))
    d_calc=NA
    se=NA
  }

  return(data.frame("df_1"=df_1,"df_2"=df_2,"tstat"=NA, "fstat"=val, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=N_from_df, "ES"=d_calc, "SE"=se))
}
```

```{r}
# for comparison between proportions 
#ex <- "prob: 13 / 14 , 2 / 14"
parse_prop <- function(propval){
  val <- str_extract_all(propval, "[0-9]+")[[1]]
  num1 <- val[1] |> as.numeric()
  den1 <- val[2] |> as.numeric()
  num2 <- val[3] |> as.numeric()
  den2 <- val[4] |> as.numeric()
  est1 <- num1/den1
  est1_var <- est1*(1-est1)/den1
  est2 <- num2/den2
  est2_var <- est2*(1-est2)/den2
  diff <- est1-est2
  diff_var <- est1_var+est2_var
  return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=diff, "SE"=sqrt(diff_var)))
}
#parse_prop(ex)

@@

```{r}
# for one proportion
#ex <- "raw prop : 10 / 18"
parse_raw_prop <- function(propval){
  val <- str_extract_all(propval, "[0-9]+")[[1]]
  num1 <- val[1] |> as.numeric()
  den1 <- val[2] |> as.numeric()
  est1 <- num1/den1
  est1_var <- est1*(1-est1)/den1
   return(data.frame("df_1"=NA, "df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=est1, "SE"=sqrt(est1_var)))
}
#parse_raw_prop(ex)
```

```{r}
parse_mean_ci <- function(mci,within_between,n){
  cond1=str_extract(mci, "m1.*\\],")
  cond2=str_extract(mci, "m2.*\\]")
  m1=str_extract(cond1, "m1=.*\\[") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\[") |> str_sub(4,-2) |> as.numeric()
  low1=str_extract(cond1, "\\[.*,.") |> str_sub(2,-3) |> as.numeric()
  low2=str_extract(cond2, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high1=str_extract(cond1, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  high2=str_extract(cond2, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se1=high1-low1/(2*1.96)
  se2=high2-low2/(2*1.96)
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se))
}
```

```{r}
parse_mean_sd <- function(msd,within_between,n){
  cond1=str_extract(msd, "m1.*\\),")
  cond2=str_extract(msd, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  sd1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  sd2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  sd_pool=(sd1+sd2)/2
  se=sd_pool/sqrt(n)
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se))
}

@@

```{r}
parse_mean_se <- function(mse,within_between,n){
  cond1=str_extract(mse, "m1.*\\),")
  cond2=str_extract(mse, "m2.*\\)")
  m1=str_extract(cond1, "m1=.*\\(") |> str_sub(4,-2) |> as.numeric()
  m2=str_extract(cond2, "m2=.*\\(") |> str_sub(4,-2) |> as.numeric()
  se1=str_extract(cond1, "\\(.*\\),") |> str_sub(2,-3) |> as.numeric()
  se2=str_extract(cond2, "\\(.*\\)") |> str_sub(2,-2) |> as.numeric()
  se=(se1+se2)/2
  tval=(m1-m2)/se |> abs()
  if (within_between=="within"){
  df=n-1
  pval=pt(q=tval, df=df, lower.tail=FALSE)*2
  d_calc=tval/(sqrt(df)) 
  }
  else if (within_between=="between"){
    df=n-2
    pval=pt(q=tval, df=df, lower.tail=FALSE)*2
    d_calc=2*tval/sqrt(df)
  }
  else{
    df=NA
    pval=NA
    d_calc=NA
  }
  return(data.frame("df_1"=df,"df_2"=NA,"tstat"=tval, "fstat"=NA, "p_calc"=pval, "d_calc"=d_calc, "N_calc"=NA, "ES"=m1-m2, "SE"=se))
}

@@

#this is just to deal with yang2018 where we have d's given and bci
#ex <- "d: 1.40 ; bci: b=1.72 [1.44, 2.00]"
parse_dbci <- function(raw_stat){
  bci = str_extract(raw_stat, ";.*") |> str_sub(2,-1)
  beta=str_extract(bci, "b=.*\\[") |> str_sub(3,-2) |> as.numeric()
  low=str_extract(bci, "\\[.*,") |> str_sub(2,-2) |> as.numeric()
  high=str_extract(bci, ",.*\\]") |> str_sub(2,-2) |> as.numeric()
  se=high-low/(2*1.96)

  dval = str_extract(raw_stat, ".*;") |> str_sub(3,-2) |> as.numeric()
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=dval, "N_calc"=NA, "ES"=beta, "SE"=se))
}
#parse_dbci(ex)

@@

do_blanks <- function(){
  return(data.frame("df_1"=NA,"df_2"=NA,"tstat"=NA, "fstat"=NA, "p_calc"=NA, "d_calc"=NA, "N_calc"=NA, "ES"=NA, "SE"=NA))
}
do_parsing=function(raw_stat, within_between,n){
  if (is.na(raw_stat)) {return (do_blanks())}
  if (str_sub(raw_stat,1,1)=="t"){return(parse_t(raw_stat, within_between))}
  if (str_sub(raw_stat,1,1)=="F"){return(parse_f(raw_stat, within_between))}
  if (str_sub(raw_stat,1,4)=="prop"){return(parse_prop(raw_stat))}
  if (str_sub(raw_stat,1,7)=="rawprop"){return(parse_raw_prop(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="MCI"){return(parse_mean_ci(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSD"){return(parse_mean_sd(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,3)=="MSE"){return(parse_mean_se(raw_stat, within_between,n))}
  if (str_sub(raw_stat, 1,8)=="wilcoxon"){return(parse_wilcoxon(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bse"){return(parse_beta_se(raw_stat))}
  if (str_sub(raw_stat, 1,3)=="bci"){return(parse_beta_ci(raw_stat))}
  if (str_sub(raw_stat, 1,1)=="d"){return(parse_dbci(raw_stat))}

@@

```
<!--
## Compare pvals

@@

Where there's a difference, I could check whether it's being compared to something *I* calculated versus something that an original paper or students paper calculated? Except that there's sources for errors in any of those. Ones where we get an off  by two error -- should I double check within-betweeness for the test? 
-->
## what didn't parse

@@

test |> filter(is.na(target_d_calc)&is.na(target_ES)) |> filter(!is.na(target_raw_stat)) |>  pull(target_raw_stat)

test |> filter(is.na(rep_d_calc)&is.na(rep_ES)) |> filter(!is.na(replication_raw_stat)) |> pull(replication_raw_stat)
```

<!--
## how are the df's lining up with sample size?

@@

```
-->
# PredInt and P_orig

d_es <-  test |> 
  mutate(target_d_calc=abs(target_d_calc),
         target_ES=abs(target_ES),
         rep_d_calc=case_when(
           same_dir=="yes" ~ abs(rep_d_calc),
           same_dir=="no" ~-abs(rep_d_calc),
           T ~ as.numeric(NA)
          ),
         rep_ES=case_when(
           same_dir=="yes" ~ abs(rep_ES),
           same_dir=="no" ~-abs(rep_ES),
           T ~ as.numeric(NA)
         ))

@@

```{r}
do_pred_int <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)){
    return(Replicate::pred_int(target_ES, target_SE**2, rep_ES, rep_SE**2)$rep.inside)
  }
  return(NA)
}

do_p_orig <- function(target_ES, target_SE, rep_ES, rep_SE){
  if(!is.na(target_ES)&!is.na(rep_ES)){
    return(Replicate::p_orig(target_ES, target_SE**2,rep_ES, t2=0, rep_SE**2))
  }
  return(NA)
}

do_subjective_rep <- function(replicated_instructor_code, replicated_report_code, adjudicated_replication_code){
  if (is.na(replicated_instructor_code)){return(as.numeric(NA))}
  if (is.na(replicated_report_code)){return(as.numeric(NA))}
  if (replicated_instructor_code==replicated_report_code){ return(replicated_instructor_code)}
  if (!is.na(adjudicated_replication_code)){return (adjudicated_replication_code)}
  return(as.numeric(NA))
}
d_es_predInt <- d_es |> 
         mutate(
           predInt=do_pred_int(target_ES, target_SE, rep_ES, rep_SE),
           p_orig=do_p_orig(target_ES, target_SE, rep_ES, rep_SE),
           sub_rep= do_subjective_rep(replicated_instructor_code, replicated_report_code, adjudicated_replication_code))

@@

#d_check_nas |> filter(if_any(everything(), ~is.na(.)))

#d_check_nas |> filter(across(everything(), ~!is.na(.)))

# d_check_nas  |> select(target_lastauthor_year, status, academic_year, target_year,
#            stanford_internal,open_data, open_materials, target_on_turk,
#            replication_on_turk, within_between, single_vignette, repeated_measure,
#            target_N, replication_N, predInt, p_orig) |>  filter(if_any(everything(), ~is.na(.)))
```

@@

TODOs:
- will need to do selection of which things have complete cases for models
- will need to z-score things (in a recoverable way)
